%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Semester Exchange} % Degree
    {University of Oslo} % Institution
    {Oslo, Norway} % Location
    {Aug. 2017 - Feb. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Semester exchange working on the Master's thesis}
      \end{cvitems}
    }
    
  \cventry
    {M.S. in Informatics} % Degree
    {Technical University of Munich} % Institution
    {Munich, Germany} % Location
    {Apr. 2018 - Jul. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Main area}: DATABASES AND INFORMATION SYSTEMS}
        \item {\textbf{Advanced Practical Course}: User-centered Design of Applications on Public Displays}
        \item {\textbf{Interdisciplinary Project in an Application Subject}: Web Interface and Solution Methods for the Vehicle Routing Problem}
        \item {\textbf{Advanced Seminar Course}: Current Topics in Recommender Systems}
        \item {\textbf{Master's thesis}: Culture-Based Opinion Mining in the Tourism Domain}
        \item {\textbf{Final grade}: 2.0}
      \end{cvitems}
    }
    
    \cventry
    {Semester Exchange} % Degree
    {University College Lilleb\ae lt} % Institution
    {Odense, Denmark} % Location
    {Aug. 2016 - Jan. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Semester exchange, taking courses and projects}
      \end{cvitems}
    }
    
    \cventry
    {B.S. in Computer Science} % Degree
    {University of Bologna} % Institution
    {Cesena, Italy} % Location
    {Sep. 2014 - Oct. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Bachelor's thesis}: Cross Organism annotation prediction through deep learning algorithms}
        \item {\textbf{Final grade}: 103}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
