%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Engineer} % Job title
    {DNB} % Organization
    {Oslo, Norway} % Location
    {Feb. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {\textbf{Profitability}: Working on data pipeline, from seeds to result, transforming with dbt. Switching from legacy ETL to more robust and modern ELT tools. Building CI/CD Pipeline with GitLab and Docker. Building pipelines to automate the creation of reports in different forms: Database table, XML, JSON, CSV, pdf}
      \item {\textbf{Wealth Management Investments}:Transfering data from PostgreSQL database to Snowflake, due to bank merge. Modifying DNB business logic and pipelines for investments and savings, so that it replicates SBanken's one.
Using Streamsets for ingestion and load, dbt for transformation, Airflow for orchestration.}
      \item {\textbf{Generic Key Management}: Working on the creation and retrieval of anonymized keys for bank customers, matching natural keys containing sensitive data. Migrating old solution to new logic with new tools and different implementation. Working with DB2, Flask, Azure DevOps Organizations, Azure Function App, Azure Key Vault, Snowflake, Python, Redis, Apache Airflow, Streamsets, Spark Expressions, Terraform}
      \item {\textbf{Polaris}: Working on the platform. Support on-boarding of different "domains" within the bank to create valuable data products. Reading data from Kafka. Using Snowflake as data warehouse. Building transformation models with DBT. Orchestrating with Airflow}
      \item {\textbf{Working with}: git, Apache Kafka, Gitlab, Azure, PostgreSQL, DB2, Teradata, Redis, Snowflake, dbt, Streamsets, Apache Airflow, Apache Spark, Docker, Python, Flask, Jira, Confluence, Apache Spark, Terraform}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer I} % Job title
    {Neonomics} % Organization
    {Oslo, Norway} % Location
    {Jul. 2022 - Jan. 2023} % Date(s)
    {
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Neonomics} % Organization
    {Oslo, Norway} % Location
    {Jul. 2021 - Jun. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working on the core functionalities of the product, in a microservices architecture, to create unified APIs for open banking in Europe, using PSD2.}
        \item {Built and deployed overall service infrastructure utilizing Docker container, CircleCI, and several AWS stack(Including EC2, ECS, Route 53, S3, CloudFront, RDS, ElastiCache, IAM), focusing on high-availability, fault tolerance, and auto-scaling.}
        \item {\textbf{Working with}: git, GCP, MySql, SQLite, CassandraDB, Liquibase, Jenkins, Apache Spark, Docker, Kubernetes, Kibana, Opensearch, Python, Jira, Confluence, Java, Java Spring, Java spark}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Technical University of Munich - Chair of Energy and Application Technology} % Organization
    {Munich, Germany} % Location
    {Oct. 2020 - May. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working on the RegHEE project (\href{https://www.epe.ed.tum.de/en/emt/research/application-areas/completed-projects/reghee/}{https://www.epe.ed.tum.de/en/emt/research/application-areas/completed-projects/reghee/})}
        \item {Development, Maintenance and Optimization of a regional energy exchange system on an Ethereum blockchain system using Python APIs}
        \item {Ended up publishing a paper with the results of the research \href{https://ietresearch.onlinelibrary.wiley.com/doi/10.1049/stg2.12058}{https://ietresearch.onlinelibrary.wiley.com/doi/10.1049/stg2.12058}}
        \item {\textbf{Working with}: git, Solidity, PostgreSQL, Python, Web3.py, Ethereum, Flask}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Associate Software Engineer} % Job title
    {CA Technologies} % Organization
    {Prague, Czech Republic} % Location
    {Dec. 2017 - Feb. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working on the backend. building and maintaining microservices with REST APIs}
        \item {\textbf{Working with}: git, MySql, Java, Python, Java Spring, Java Springboot, Junit}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {NewTeam S.r.l.} % Organization
    {Cesena, Italy} % Location
    {Mar. 2017 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Building a query builder using DevExpress to allow users to create and save their own personalized queries through a GUI}
        \item {\textbf{Working with}: git, MS Sql, Asp.Net, C\#, JavaScript}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Bygkontrol} % Organization
    {Odense, Denmark} % Location
    {Nov. 2016 - Jan. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Building a distributed system converting polar coordinates to .fbx, for autocad. Comparing generated file with the one of the project}
        \item {\textbf{Working with}: git, MS Sql, Asp.Net, C\#}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
